---
title: "remlTemplate"
author: "SRE"
date: "March 14, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# 2018-12-16 (knb-lter-cap.636.6)

* functionalized tower_data_upload.R
* remove formatting from methods
* reconstruct coverage to rOpenSci EML v2


# 2018-06-05 (knb-lter-cap.636.5)

Workflow moved to Rmd for the 2018-06-05 update.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eml-2.1.1, include=FALSE}
emld::eml_version("eml-2.2.0")
# options("emld_db" = "eml-2.1.1")
# emld::eml_version("eml-2.1.1")
```

```{r libraries}
library(EML)
library(RPostgreSQL)
library(RMySQL)
library(tidyverse)
library(tools)
library(readxl)
library(aws.s3)
library(capeml)
library(gioseml)
```

```{r dataset_details}
projectid <- 636
packageIdent <- 'knb-lter-cap.636.6'
pubDate <- as.character(Sys.Date())
```
 
```{r helper_functions}
source('~/localRepos/reml-helper-tools/amazon_file_upload.R')
```

```{r connections::amazon}
source('~/Documents/localSettings/aws.s3')
```

```{r connections::postgres::local, eval=FALSE}
source('~/Documents/localSettings/pg_local.R')
pg <- pg_local
```

```{r connections::postgres::prod, eval=T }
source('~/Documents/localSettings/pg_prod.R')
pg <- pg_prod
```

```{r connections::mysql::prod, eval=T }
source('~/Documents/localSettings/mysql_prod.R')
mysql_prod <- mysql_prod_connect()
```

# CAREFUL WITH ATTRS - AT THE TIME OF THIS WRITING, MULTIPLE MISSING VALUE CODES ARE NOT SUPPORTED FROM THE TEMPLATE, SO NAs and NaNs NEED TO BE ADDRESSED BY HAND (AS DO NAs GENERALLY EVEN WHEN ALONE)

```{r LDP}

tower_data_ldp <- dbGetQuery(pg,
'SELECT
  "timestamp",
  airtc_avg,
  rh, slrkw_avg,
  slrmj_tot,
  ws_ms_avg,
  wind_dir,
  rain_mm_tot
FROM lter120.ldp_data;')

tower_data_ldp <- tower_data_ldp %>%
  mutate(site_code = "Lost Dutchman State Park (LDP)") %>%
  select(site_code, timestamp:rain_mm_tot) %>%
  arrange(timestamp)

write_attributes(tower_data_ldp)
# write_factors(tower_data_ldp) # factors not present

tower_data_ldp_desc <- 'Micrometeoroligical data from the CAP LTER weather station located at the Lost Dutchman State Park, AZ. Data are 10-min averages of measurments collected at 5-second intervals.'

tower_data_ldp_DT <- create_dataTable(dfname = tower_data_ldp,
                                      description = tower_data_ldp_desc,
                                      dateRangeField = 'timestamp')

```

# CAREFUL WITH ATTRS - AT THE TIME OF THIS WRITING, MULTIPLE MISSING VALUE CODES ARE NOT SUPPORTED FROM THE TEMPLATE, SO NAs and NaNs NEED TO BE ADDRESSED BY HAND (AS DO NAs GENERALLY EVEN WHEN ALONE)

```{r DBG}

tower_data_dbg <- dbGetQuery(pg,
'SELECT
  "timestamp",
  airtc_avg,
  rh, slrkw_avg,
  slrmj_tot,
  ws_ms_avg,
  wind_dir,
  rain_mm_tot
FROM lter120.dbg_data;')

tower_data_dbg <- tower_data_dbg %>%
  mutate(site_code = "Desert Botanical Garden (DBG)") %>%
  select(site_code, timestamp:rain_mm_tot) %>% 
  arrange(timestamp)

write_attributes(tower_data_dbg)
# write_factors(tower_data_dbg) # factors not present

tower_data_dbg_desc <- "Micrometeoroligical data from the CAP LTER weather station located near the Desert Botanical Garden in Papago Park, AZ. Data are 10-min averages of measurments collected at 5-second intervals."

tower_data_dbg_DT <- create_dataTable(dfname = tower_data_dbg,
                                      description = tower_data_dbg_desc,
                                      dateRangeField = 'timestamp')

```

```{r title}

title <- 'CAP LTER weather stations at Papago Park and Lost Dutchman State Park in the greater Phoenix metropolitan area, ongoing since 2010'
```

```{r abstract}

abstract <- set_TextType("abstract.md")
```

```{r connections::mysql::prod redux, eval=T }
source('~/Documents/localSettings/mysql_prod.R')
mysql_prod <- mysql_prod_connect()
```

```{r people}


jonAllen <- create_role(firstName = 'jon', lastName = 'allen', roleType = 'creator')
nancyGrimm <- create_role(firstName = 'n', lastName = 'grimm', roleType = 'creator')
sharonHall <- create_role(firstName = 'shar', lastName = 'hall', roleType = 'creator')
jasonKaye <- create_role(firstName = 'jaso', lastName = 'kaye', roleType = 'creator')
dan <- create_role(firstName = 'dan', lastName = 'child', roleType = 'creator')

creators <- list(
  nancyGrimm,
  sharonHall,
  jasonKaye,
  jonAllen,
  dan
)

stevanEarl <- create_role(firstName = 's', lastName = 'earl', roleType = "metadata")
quincyStewart <- create_role(firstName = 'q', lastName = 'stewart', roleType = "metadata")
sallyWittlinger <- create_role(firstName = 's', lastName = 'wittlinger', roleType = "metadata")
kristinGodbeer <- create_role(firstName = 'k', lastName = 'godbeer', roleType = "metadata")

metadataProvider <- list(stevanEarl,
                         quincyStewart,
                         sallyWittlinger,
                         kristinGodbeer)
```

```{r keywords}

# CAP IRTs for reference (be sure to include these as appropriate):
# https://sustainability.asu.edu/caplter/research/

write_keywords()
keywords <- create_keywordSet('keywords.csv')

```

```{r methods}

methods <- set_methods("methods.md")
```

```{r coverages}

# begin date will never change, but pull max date from data
ldp_max_date <- dbGetQuery(pg, "SELECT MAX(timestamp) AS date FROM lter120.ldp_data;")
dbg_max_date <- dbGetQuery(pg, "SELECT MAX(timestamp) AS date FROM lter120.dbg_data;")
enddate <- max(ldp_max_date$date, dbg_max_date$date) 
enddate <- as.character(enddate, format = "%Y-%m-%d")

# LDP geographic

ldpCoords <- EML::eml$boundingCoordinates(
  westBoundingCoordinate = "-111.4795",
  eastBoundingCoordinate = "-111.4789",
  northBoundingCoordinate = "33.4626",
  southBoundingCoordinate = "33.4622")

ldpGeo <- EML::eml$geographicCoverage(
  geographicDescription = "CAP LTER site at Lost Dutchman State Park",
  boundingCoordinates = ldpCoords,
  id = "geographicCoverage.LDP"
)

# DGB geographic

dbgCoords <- EML::eml$boundingCoordinates(
  westBoundingCoordinate = "-111.9476",
  eastBoundingCoordinate = "-111.9415",
  northBoundingCoordinate = "33.4612",
  southBoundingCoordinate = "33.4554")

dbgGeo <- EML::eml$geographicCoverage(
  geographicDescription = "CAP LTER site at the Desert Botanical Garden",
  boundingCoordinates = dbgCoords,
  id = "geographicCoverage.DBG")

# dbgGeo$boundingCoordinates <- dbgCoords

towerBegin <- EML::eml$beginDate(calendarDate = "2006-05-10")
towerEnd <- EML::eml$endDate(calendarDate = enddate)
towerRange <- EML::eml$rangeOfDates(beginDate = towerBegin, endDate = towerEnd)
towerTemporal <- EML::eml$temporalCoverage(rangeOfDates = towerRange)

coverage <- EML::eml$coverage(
  geographicCoverage = list(ldpGeo, dbgGeo),
  temporalCoverage = towerTemporal 
)

```

```{r construct-dataset}

# from capeml package:
# address
# publisher
# contact
# rights
# distribution

# DATASET
dataset <- EML::eml$dataset(
  title = title,
  creator = creators,
  pubDate = pubDate,
  metadataProvider = metadataProvider,
  intellectualRights = capRights,
  abstract = abstract,
  keywordSet = keywords,
  coverage = coverage,
  contact = capContact, # cap contact
  publisher = capPublisher, # cap pub
  # contact = giosContact, # gios contact
  # publisher = giosPublisher, # gios pub
  methods = methods,
  project = capProject, # cap project
  distribution = create_distribution(packageIdent))

# add associatedParty if relevant
# dataset$associatedParty <- list() 

```


```{r dataSet$dataTable}

# add dataTables if relevant

print(ls(pattern = "_DT"))

if (length(ls(pattern = "_DT")) > 0) {
  
  listOfDataTables <- lapply(ls(pattern = "_DT"), function(DT) { get(DT) } )
  
  dataset$dataTable  <- listOfDataTables  
  
}
```

```{r custom_units, eval=FALSE}

custom_units <- rbind(
  data.frame(id = "kilowattPerMeterSquared",
             unitType = "irradiance",
             parentSI = "wattPerMeterSquared",
             multiplierToSI = "1000",
             description = "average amount of energy per square meter of surface during the observation period"),
  data.frame(id = "megajoulePerMeterSquared",
             parentSI = "joulePerMeterSquared",
             unitType = "irradiance",
             multiplierToSI = "1000000",
             description = "total amount of energy per square meter of surface during the observation period"))

unitList <- set_unitList(custom_units,
                         as_metadata = TRUE)

```

```{r construct_eml, eval=TRUE}

if(exists('unitList')) {
  
  eml <- EML::eml$eml(
    access = lterAccess,
    dataset = dataset,
    additionalMetadata = unitList,
    packageId = packageIdent,
    system = "knb",
    scope = "system"
  )
  
} else {
  
  eml <- EML::eml$eml(
    access = lterAccess,
    dataset = dataset,
    packageId = packageIdent,
    system = "knb",
    scope = "system"
  )
}

```

```{r write_eml}

# write the eml to file
write_eml(eml, paste0(packageIdent, ".xml"))
```

```{r preview_data_file_to_upload}

# preview data set files that will be uploaded to S3
list.files(pattern = paste0(projectid, "_"))
```

```{r upload_data_S3}

# upload files to S3
lapply(list.files(pattern = paste0(projectid, "_")), dataToAmz)
```

```{r clean_up}

# remove data files
dataFilesToRemove <- dir(pattern = paste0(projectid, "_"))
file.remove(dataFilesToRemove)

# EML to S3
if(length(list.files(pattern = "*.xml")) == 1) {
  emlToAmz(list.files(pattern = "*.xml")) } else {
    print("more than one xml file found")
  }

# EML to cap-data-eml and remove file from project
tryCatch({
  
  if(length(list.files(pattern = "*.xml")) == 1) {
    file.copy(list.files(pattern = "*.xml"), "/home/srearl/localRepos/cap-metadata/cap-data-eml/")
    file.remove(list.files(pattern = "*.xml")) } else {
      print("more than one xml file found")
    }
},
warning = function(warn) {
  print(paste("WARNING: ", warn))
},
error = function(err) {
  print(paste("ERROR: ", err))
  
}) # close try catch
```
